%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge \scshape Adam Deryło} \\ \vspace{4pt}
  % al.Niepodleglosci 165 m.31, Warsaw, Poland  \\ \vspace{1pt}
  \small \raisebox{-0.1\height}\faPhone\ +48 698 608 344 ~ \href{mailto:a.m.derylo@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{a.m.derylo@gmail.com}} ~
  \href{https://linkedin.com/in//adamderylo}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/adamderylo}}  ~
  \href{https://github.com/aderylo}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/aderylo}}
  % \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

% TUM - all accolades
\resumeSubheading
{Technical University of Munich}{Oct. 2024 -- Ongoing}
{Masters of Informatics}{Munich, Germany}
\resumeItemListStart
\resumeItem{Best technical univeisty in Germany according to the QS ranking.}
\resumeItemListEnd

% UW - all accolades
\resumeSubheading
{Warsaw University}{Oct. 2020 -- Jul. 2024}
{Double degree: BSc in Computer Science \& BSc in Cognitive Science}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{Top-rated CS undergraduate program in Poland according to the QS ranking.}
\resumeItem{1st-year modules: Functional Programming, OOP, C, Introduction to AI, Linear Algebra.}
\resumeItem{2nd-year modules: Adv. Algorithms, Databases, Computer networks, Web Apps, Statistics, NLP.}
\resumeItem{3rd-year modules: Distributed systems, Concurrency theory,  Security of computer systems.}
\resumeItem{Rector's scholarship for academic achievements.}
\resumeItemListEnd

\resumeSubheading
{2SLO High School}{Sep. 2017 -- May. 2020}
{Computer Science, Mathematics \& Philosophy profile}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{Top-4 rated high school in Poland according to the Perspektywy ranking.}
\resumeItem{Laureate of the 2018 Polish Olympiad in Philosophy for high school students.}
\resumeItem{Scholarship for outstanding academic achievements.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% Amazon
\resumeSubheading
{Amazon}{Jun. 2024 - Sep. 2024}
{Software Engineering Intern | AWS CDK, Typescript, React, Python}{Madrid, Spain}
\resumeItemListStart
\resumeItem{NintAi, applied science team, responsible for providing ML modles for visual navigaiton.}
\resumeItem{Developed and deployed a UI for a ML inference platform, which facilitates image search at Amazon.}
\resumeItem{Implemented UI infrastructure using AWS CodePipeline, CodeBuild, API Gateway, Lambda, SIGV4 Auth, ect.}
\resumeItem{Established end-to-end testing with NightwatchJS and Selenium Grid, integrating it into the CI/CD pipeline.}
\resumeItemListEnd

% TSMC - all
\resumeSubheading
{Taiwan Semiconductor Manufacturing Company}{Jul. 2023 - Sep. 2023}
{Software Engineering Intern | Pytorch, Huggingface, Scikit-learn, Python}{Hsinchu, Taiwan}
\resumeItemListStart
\resumeItem{AI Application and Platform Development Team responsible for the automation of fab processes.}
\resumeItem{Developed custom BLIP2 based model for photomask defect classification and dataset bootstrapping.}
\resumeItem{Ranked in the top 8 out of 80+ Interns in the final competition.}
\resumeItemListEnd

% GS - all
\resumeSubheading
{Goldman Sachs}{Jun. 2022 - Aug. 2022}
{Summer Analyst $|$ Redis, Java, Procmon, Golang }{Stockholm, Sweden}
\resumeItemListStart
\resumeItem{Global reconciliations team, daily processing of 80+ mln trade \& position data entries.}
\resumeItem{Collaborated on optimizing caching performance and reliability of data loading processes.}
\resumeItem{Worked on extending database performance limits with intelligent cache priming based on Change Data Capture.}
\resumeItem{Developed Redis cache monitoring tool suite to speed up emergency debug and development cycle.}
\resumeItemListEnd

% Respo.Vision - all
\resumeSubheading
{ReSpo.Vision}{Jul. 2021 - May. 2022}
{Software Engineer Intern $|$  Python, Postgre, Git, SQL, Pytorch}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{40+ sprints under the Scrum development framework in a rapidly growing team.}
\resumeItem{Worked on a back-end implementation of a betting hints generator that withstood 100k API calls daily.}
\resumeItem{Created a deep learning NLP module using architectures such as BERT.}
\resumeItem{NLP module tackled the problem of context-dependent noun declination in Slavic languages.}
\resumeItemListEnd

\resumeSubheading
{Bain \& Company}{Mar. 2021 - Apr. 2021}
{Spring Intern $|$ Nielsen, Ipsos, Bain's overlay for MS Office}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{Supported a consulting team in the area of wood market data analysis.}
\resumeItem{Collaborated on a business case under the supervision of a dedicated mentor.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Bachelor thesis at Nencki Institute} $|$ \emph{Python, Pytorch, Tianshou, SLURM, Wandb} }{Nov. 2023 - Oct. 2024}
\resumeItemListStart
\resumeItem{Collaborated on computational neuroscience research at the Nencki Institute of Experimental Biology.}
\resumeItem{Co-developed a novel reinforcement learning model of the dopaminergic circuit.}
\resumeItem{Conducted experiments on HPC cluster, using SLURM for scheduling and Wandb for monitoring.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Bachelor thesis at NVIDIA} $|$ \emph{C++, CUDA, CMake, Python}}{Oct. 2022 - Jun. 2023}
\resumeItemListStart
\resumeItem{Worked with NVIDIA DALI team on accelerating image decompression in ML astronomy workflows.}
\resumeItem{Contributed module to the open-source DALI library, improving the performance of the FITS decoder.}
\resumeItem{Devised a testing \& profiling pipeline to allow for benchmarking various CUDA kernel optimizations.}
\resumeItem{Showcased the result by rewriting NASA Coronal Hole Semantic Segmentation pipeline and achieving 70\% speedup.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ELF Binary Reconstruction Tool} $|$ \emph{C++, Assembly, ELF Format, Reverse Engineering}}{Feb. 2024 - Apr. 2024}
\resumeItemListStart
\resumeItem{Developed a program to reconstruct relocation tables and symbols from stripped ELF executables.}
\resumeItem{Implemented heuristic algorithms for function boundary detection and instruction classification.}
\resumeItem{Designed solution for i386 architecture binaries compiled for Intel Quark microcontrollers.}
\resumeItem{Such reconstruction allows for modifying parts of compiled code without hassles of full decompilation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Hearts Game Server} $|$ \emph{C, TCP/IP, Multithreading, Protocol Design}}{Apr. 2024 - May 2024}
\resumeItemListStart
\resumeItem{Implemented a TCP server for Hearts game, directly using system calls for networking needs}.
\resumeItem{Developed robust serialization and deserialization of socket data with timeout mechanics.}
\resumeItem{Created a flexible game engine capable of handling various Hearts rule variations.}
\resumeItem{Applied concepts from Beej's Guide to optimize server performance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Deep Neural Networks} $|$ \emph{Python, Pytorch, Tensorboard}}{Nov. 2023 - Jan. 2024}
\resumeItemListStart
\resumeItem{Recreated implementations of 4 breakthrough ML papers from scratch.}
\resumeItem{Implemented following papers from scratch: 
\begin{list}{$\circ$}{}
  \item "The Reversible Residual Network: Backpropagation Without Storing Activations"
  \item "PaDiM: a Patch Distribution Modeling Framework for Anomaly Detection and Localization"
  \item "Attention is all you need"
  \item "Bigger, Better, Faster: Human-level Atari with human-level efficiency"
\end{list} }
\resumeItem{Scored highest mark awarded to the best 5\% of course participants.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{C interpreter} $|$ \emph{Haskell, GHC, Cabal, BNFC}}{Apr. - Jun 2023}
\resumeItemListStart
\resumeItem{Created an interpreter for a C-like language, called Latte.}
\resumeItem{Implemented support for scoping, functions, multidimensional arrays, classes and many more.}
\resumeItem{Utilized monad transformers to create various features such as garabage collection mechanism for the language.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Minix OS} $|$ \emph{C, Quemu, Bash, rsync}}{Apr. - Jun. 2023}
\resumeItemListStart
\resumeItem{Developed various custom features for the Minix OS, including modifying the kernel.}
\resumeItem{Implemented theoretically optimal scheduler, improving the performance of the system.}
\resumeItem{Devised an add-on for the virtual file system which introduced file exclusivity mechanism.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{BEST hacking league} $|$ \emph{React, Python, OpenAI Playground}}{Apr. 2023}
\resumeItemListStart
\resumeItem{Earned 2nd place in a hackathon organized by the Board of European Students of Technology.}
\resumeItem{Developed a voice assistant for Warehouse 4.0 workers.}
\resumeItem{Extended LLM knowledge base by leveraging a NoSQL database, improving query handling for warehouse layout.}
\resumeItem{Devised intelligent prompting for a voice assistant, improving context awareness and user experience.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Distributed alerting system} $|$ \emph{Grpc, Google Cloud Platform, Python}}{Nov. 2022 - Jan. 2023}
\resumeItemListStart
\resumeItem{Developed scalable microservice system for monitoring services and running complex alerting routines.}
\resumeItem{Utilized GRPC, PubSub queues, Cloud SQL and other tools to satisfy SLO requirements for 10k services.}
\resumeItem{Project supervised by Google employees.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Goldman Sachs EMEA 2022 Hackathon} $|$ \emph{Python, Flask, Git}}{Nov. 2022}
\resumeItemListStart
\resumeItem{Achieved first place during a challenging 24-hour hackathon.}
\resumeItem{Designed and implemented a web portal aimed at enhancing Goldman Sachs' recruitment efforts.}
\resumeItem{Implemented a stock market simulation game as one of the features.}
\resumeItem{Contributed to the development of a 3D render for a physical token with a link to the portal.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{N-dimensional labyrinth solver} $|$ \emph{C, Valgrind, Cmake,  Git}}{Jun. 2022}
\resumeItemListStart
\resumeItem{Developed a high-performance traverser for multidimensional mazes/large graphs.}
\resumeItem{Utilized most memory efficient solution by incorporating 2-bit BFS algorithm.}
\resumeItem{Implemented arbitrary large integer type to facilitate enormous labyrinths and showcase memory efficiency.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Concurrent Unix-like directory} $|$ \emph{C, Pthreads, Helgrind, Cmake,  Git}}{Jan. 2022}
\resumeItemListStart
\resumeItem{Implemented add-ons to the file system, which allowed for concurrent creation, deletion and movement of files. }
\resumeItem{Utilized tailored-made readers-writers lock with Latest Common Ancestor writer locking.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Enhancing Splay Tree for pattern search} $|$ \emph{C++, Catch2, Cmake, Bash, Git}}{Dec. 2021}
\resumeItemListStart
\resumeItem{Developed an algorithm for efficient search of patterns in DNA sequence.}
\resumeItem{Utilized a splay tree data structure enhanced with attributes updated through lazy propagation.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------Extracurricular------------
\section{Extracurricular}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Member}{, Bain \& Company Champions Class 2023} \\
                \textbf{2nd Place}{, PSDC 2020 debating championship, preliminary stage to World Schools Debating Championship.} \\
                \textbf{Laureate}{, 8/1000+ in the 31st National Philosophy Olympiad} \\
          }}
\end{itemize}
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Programming Languages}{: Python, Java, C/C++, JavaScript, R,  Ocaml, Go, SQL} \\
                \textbf{Technologies}{: Git, Fedora/Ubuntu/Debian, Jira, Redis, Docker, Pydantic, React, Cloud Run} \\
                \textbf{Natural languages}{: English (C2), Polish (Native), Spanish (B1) } \\
          }}
\end{itemize}
\vspace{-16pt}

\end{document}

